---
title: "outputs"
author: "Daniel Chen"
date: "04/22/2014"
output: html_document
---
# Plotting Function
```{r}
plot.thesis.data <- function(data, numAgents, numTimeTicks)
  {
  x <- read.csv(data, header=FALSE, stringsAsFactors=FALSE)

  names(x) <- c("time", "agent",
                       "p1", "p2", "p3", "p4", "p5",
                       "n1", "n2", "n3", "n4", "n5")

  print(head(x, numAgents))
  print(tail(x, numAgents))

  for (i in 3:12) {
    x[ ,i] <- as.numeric(x[ ,i])
  }

  x.1 <- x[seq(1, numTimeTicks * numAgents ,numAgents),]
  x.2 <- x[seq(2, numTimeTicks * numAgents ,numAgents),]
  x.3 <- x[seq(3, numTimeTicks * numAgents ,numAgents),]
  x.4 <- x[seq(4, numTimeTicks * numAgents ,numAgents),]
  x.5 <- x[seq(5, numTimeTicks * numAgents ,numAgents),]

  x.1.ave.pos <- apply(x.1[,c(3,4,5,6,7)],1, mean)
  x.1.ave.neg <- apply(x.1[,c(8,9,10,11,12)],1,mean)

  x.2.ave.pos <- apply(x.2[,c(3,4,5,6,7)],1,mean)
  x.2.ave.neg <- apply(x.2[,c(8,9,10,11,12)],1,mean)

  x.3.ave.pos <- apply(x.3[,c(3,4,5,6,7)],1,mean)
  x.3.ave.neg <- apply(x.3[,c(8,9,10,11,12)],1,mean)

  x.4.ave.pos <- apply(x.4[,c(3,4,5,6,7)],1,mean)
  x.4.ave.neg <- apply(x.4[,c(8,9,10,11,12)],1,mean)

  x.5.ave.pos <- apply(x.5[,c(3,4,5,6,7)],1,mean)
  x.5.ave.neg <- apply(x.5[,c(8,9,10,11,12)],1,mean)

  plot(x.1.ave.pos,lty=1,col=1,type="b",ylim=c(0,1))
  lines(x.1.ave.neg, lty=2, col=1, type="b", lwd=3)

  lines(x.2.ave.neg,ylim=c(0,1),lty=1,col=2,type="b")
  lines(x.2.ave.neg,lty=2,col=2,type="b", lwd=3)

  lines(x.3.ave.neg,lty=1,col=3,type="b")
  lines(x.3.ave.neg,lty=2,col=3,type="b", lwd=3)

  lines(x.4.ave.neg,lty=1,col=4,type="b")
  lines(x.4.ave.neg,lty=2,col=4,type="b", lwd=3)

  lines(x.5.ave.neg,lty=1,col=5,type="b")
  lines(x.5.ave.neg,lty=2,col=5,type="b", lwd=3)
  }
```

# Sanity Case:
- Agents Activated: Agent 1 ont
- Valence Bank: positive only
    - Valence bank activation: 1's
- Valence bank Weights: random
    - opposite 0
    - corresponding 0
    - carry over = 0.2
    - bias = 0
    - decay = -0.5
- Network: circle

```{r}
plot.thesis.data("/home/dchen/git/repast-neural-network-agent-based-model/R/data/agent1pos1.csv", 10, 10)
```

# Sanity Case:
- Agents Activated: Agent 1 only
- Valence Bank: positive only
    - Valence bank activation: **random**
- Valence bank Weights: random
    - opposite 0
    - corresponding 0
    - carry over = 0.2
    - bias = 0
    - decay = -0.5
- Network: circle


```{r}
plot.thesis.data("/home/dchen/git/repast-neural-network-agent-based-model/R/data/agent1posrandom.csv", 10, 10)
```

# Sanity Case:
- Agents Activated: Agent 1 only
- Valence Bank: **both**
    - Valence bank activation: random
- Valence bank Weights: random
    - opposite 0
    - corresponding 0
    - carry over = 0.2
    - bias = 0
    - decay = -0.5
- Network: circle

```{r}
plot.thesis.data("/home/dchen/git/repast-neural-network-agent-based-model/R/data/agent1bothrandom.csv", 10, 10)
```

# Sanity Case:
- Agents Activated: Agent 1 only
- Valence Bank: both
    - Valence bank activation: random
- Valence bank Weights: random
    - opposite **-0.2**
    - corresponding **0.5**
    - carry over = 0.2
    - bias = 0
    - decay = -0.5
- Network: circle

```{r, echo=FALSE}
plot.thesis.data("/home/dchen/git/repast-neural-network-agent-based-model/R/data/agent1bothrandom-weights.csv", 10, 10)
```

# Sanity Case:
- Agents Activated: **All**
- Valence Bank: both
    - Valence bank activation: random
- Valence bank Weights: random
    - opposite -0.2
    - corresponding 0.5
    - carry over = 0.2
    - bias = 0
    - decay = -0.5
- Network: circle

```{r, echo=FALSE}
plot.thesis.data("/home/dchen/git/repast-neural-network-agent-based-model/R/data/randomvaluesetweight.csv", 10, 10)
```

# Output Data
- Agents Activated: 1
- Valence Bank: both
    - Valence bank activation: random
- Valence bank Weights: random
    - opposite -0.2
    - corresponding 0.5
    - carry over = 0.2
    - bias = 0
    - decay = -0.5
- Network: circle
- random number: read in from file

- Processing units per valence bank: 5
- number of agents: 10
- number of time ticks: 10,000

```{r, echo=FALSE}
plot.thesis.data("/home/dchen/git/repast-neural-network-agent-based-model/R/data/agent1-both-random-weights-10k.csv", 10, 10000)
```
